Title Goes Here

### 2020-02-25 paper/paper.tex
Better formatting for type equality symbol
Improved some wording

\newcommand{\typeeq}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}\,}

@@

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given representation in terms of \ttt{Either}, \ttt{(,)},
\ttt{()} and \ttt{Void}. This "standardized" type representation is
given by \ttt{ERepTy T}. \ttt{ERepTy} is an type family associated to
the type class \ttt{ERep}. This type will be called the \textit{canonical type}
of \ttt{T}.

@@

Given this code, \ttt{ERep ComplexPair \typeeq (Complex Double, Complex Double)}. Here
is an example that demonstrates why this is more useful than if it *fully* deconstructed
each type into \ttt{Either}s and \ttt{(,)}:

@@

If \ttt{ERep ComplexPair} was fully deconstructed into
\ttt{((Double, Double), (Double, Double))}, we would need a \ttt{Num}
instance for \ttt{(Double, Double)}.
What we really want is to use the \ttt{Num} instance that already
exists for \ttt{Complex Double}, and this is what preserving this type
information allows us to do.

@@

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start, yshift=-0.5cm]{($D, T, T'$) Transform tail recursion of definitions that have a mark (when applicable)};
  \node (findmark) [process, below of=tailrec, yshift=-0.5cm]{($C^*$) Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{($C$) Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{($C$) Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{($C$) Wrap with \ttt{Construct} and \ttt{ConstructAp}};

>>>>

\newcommand{\typeeq}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}\,\;}

@@

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given a representation in terms of \ttt{Either}, \ttt{(,)}, \ttt{()}
and \ttt{Void}.  This "standardized" type representation is given by \ttt{ERepTy
T}. \ttt{ERepTy} is an type family associated to the type class \ttt{ERep}. This
type will be called the \textit{canonical type} of \ttt{T}.

@@

Given this code, \ttt{ERep ComplexPair \typeeq (Complex Double, Complex Double)}. Here
is an example that demonstrates why this is more useful than if it \textit{fully} deconstructed
each type into \ttt{Either}, \ttt{(,)} and \ttt{()}:

@@

If \ttt{ERep ComplexPair} were fully deconstructed into \ttt{((Double, Double),
(Double, Double))}, we would need a \ttt{Num} instance for \ttt{(Double,
Double)}.  What we really want is to use the fact that a \ttt{Num} instance
already exists for \ttt{Complex Double}. This is exactly what preserving this
type information allows us to do.

@@

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start, yshift=-0.5cm]{($D, T_{\ttt{f}}, T'_{\ttt{f}}$) Transform tail recursion of definitions that have a mark (when applicable)};
  \node (findmark) [process, below of=tailrec, yshift=-0.5cm]{($C^*$) Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{($C$) Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{($C$) Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{($C$) Wrap with \ttt{Construct} and \ttt{ConstructAp}};
